Supporting Information : Effect of copula on extinction risk

### 2019-02-25 SuppMat.Rmd
bug fixed : pennycuick : min limit of r to get +ve eqm. pt.

rng1<-runif(10000,min=1,max=r_bf_pennycuick) #r must be > 1 for +ve eqm pt.
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_pennycuick)
q2<-abs(unname(qr1[2])-rc_pennycuick)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

@@

    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@

```{r sim_pennycuick_scl_0.6, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"
numsims<-10000
numsteps<-25
numlocs<-5
a<-a_pennycuick
b<-b_pennycuick
scl<-0.6

rng1<-runif(10000,min=1,max=r_bf_pennycuick) #r must be > 1 for +ve eqm pt.
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_pennycuick)
q2<-abs(unname(qr1[2])-rc_pennycuick)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

if(vxx>1e-10){
  warning("Not equal spacing in rlist : Pennycuick model !!!",immediate.=T,call.=T)
}

    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

```{r fig_pennycuick_scl_0.6, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=12)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,1.5))

```{r fig_pennycuick_extrisk_d0_scl_0.6, echo=F,results="hide"}
set.seed(seed)
numsims<-10000
pennycuick_extrisk_d0<-readRDS(paste(resloc,"pennycuick_extrisk_d0.RDS",sep=""))

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=0.6) with local dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp_msmith_r_vary}](./Results/pennycuick_scl_0.6/pennycuick_ext_risk_local_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model : a = 0.1, b = 0.1, scl=0.6) with global dispersion; numlocs=5, numsteps=25, numsims=10000\label{fig_risk_global_disp_msmith_r_vary}](./Results/pennycuick_scl_0.6/pennycuick_ext_risk_global_disp.pdf){ width=40%, height=40% }

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Pennycuick model with no dispersion : rc=4.3231657); numlocs=5, numsteps=25, numsims=10000, scl=0.6\label{fig_pennycuick_risk_d0}](./Results/pennycuick_scl_0.6/pennycuick_extrisk_d0.pdf){ width=40%, height=40% }

>>>>

rng1<-runif(10000,min=(1+exp(-a)),max=r_bf_pennycuick) # for +ve eqm pt.
qr1<-quantile(rng1,probs=c(.025,.975))
q1<-abs(unname(qr1[1])-rc_pennycuick)
q2<-abs(unname(qr1[2])-rc_pennycuick)
qs<-c(q1,q2)
iqmin<-which.min(qs)
iqmax<-which.max(qs)

@@

    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@
